
%%
% Options

%% Compile with LuaLaTeX for best results
\documentclass[10pt,a4paper]{altacv}

\geometry{left=1cm,right=9cm %right column size+1.2
,marginparwidth=6.8cm %right column size
,marginparsep=1.2cm,top=1cm,bottom=1cm}

% Links
\usepackage{hyperref}

\setmainfont{Lato}

% COLORS
\definecolor{VividPurple}{HTML}{2E64FE}
\definecolor{SlateGrey}{HTML}{2E2E2E}
\definecolor{LightGrey}{HTML}{666666}
\colorlet{heading}{VividPurple}
\colorlet{accent}{VividPurple}
\colorlet{emphasis}{SlateGrey}
\colorlet{body}{LightGrey}

% the bullets for itemize and rating marker for \cvskill
\renewcommand{\itemmarker}{{\small\textbullet}}
\renewcommand{\ratingmarker}{\faCircle}

%%%%%%%%
% HEADER
\begin{document}
\name{Mathieu Béligon} \tagline{Agile Prototyper \& Developer}

\personalinfo{
  \email{mathieu.beligon@student.ecp.fr}
  \phone{+33 6 20 37 02 86}
  \location{Paris, France}
  \linkedin{\url{linkedin.com/in/mathieuBeligon}}
%  \mailaddress{1230 East Alexander Ave, Merced, CA 95340}
%  \homepage{grantalexandermorgan.github.io/}
%  \github{}
%  \printinfo{symbol}{detail}
}
\personalpitch{Master of engineering student looking for a 6-month internship as part of the requirement of the Digital Tech Year. Hightly interrested in solving complexes challenges that migh require new solutions.}

% print header
\begin{adjustwidth}{}{-8cm}
  \makecvheader
\end{adjustwidth}


%%%%%%%%%%%%%%%%%
% Work Experience
\cvsection[sidebar]{Experience}

% DTY

\cvevent{Agile prototyping}{\textsc{@ParisDigitalLab} Incubator}{Sept 2018 -- Ongoing}{Paris, France}
Develop three minimum viable products in a 7-week constraints for real-world businesses, using scrum method.
% \begin{itemize}
%   \item Project 1
%   \item Project 2
%   \item Project 3
% \end{itemize}

{\textbf{Tech:}}\space{\small \cvtag{Angular 5} \cvtag{NodeJS} \cvtag{React}}

\divider

% RAID

\cvevent{IT Manager}{@RaidCentraleSupélec}{May 2017 - May 2018}{Paris, France}
The Raid CentraleSupélec is a student association organizing 2 major sport events.
\begin{itemize}
  \item Develop and maintain 4 websites \url{https://raidcs.com} ;
  \item Develop a ranking tool for the races (needed to work with optional loops, orienteering ...).
\end{itemize}
{\textbf{Tech:}}\space{\small \cvtag{CSS 3} \cvtag{HTML 5} \cvtag{Latex} \cvtag{Php} \cvtag{Python} \cvtag{Symfony} \cvtag{Wordpress}}

\divider

% CROC

\cvevent{Robot Competition}{@Eurobot France}{May 2018}{France}
Build an autonomous Robot that would perform a set of actions against an opponent in time.

Team position: 92\textsuperscript{e}/133.

{\textbf{Tech:}}\space{\small \cvtag{Arduino} \cvtag{IA} \cvtag{SpaceClaim}}

\divider

% SWERC

\cvevent{Competitive Programmer}{@SWERC, Southwestern Europe Regional Contest}{Nov 2016}{Porto, Portugal}
Find optimized solutions for a set of complex problems in 5 hours, by team of 3 students.

Team position: 21\textsuperscript{e}/60.

{\textbf{Skills:}}\space{\small \cvtag{Algorithms} \cvtag{C++} \cvtag{Optimization} \cvtag{Segment trees} \cvtag{Union Find}}



%%%%%%
% TECH

\cvsection{Tech Skills}

\cvskills{\faFirefox}{Web}{
 {Angular 5}, {Bootstrap}, {Bulma}, {CSS 3}, {HTML 5}, {Javascript}, {Jquery}, {NodeJs}, {Php}, {Symfony}, {Wordpress}
}

\divider

\cvskills{\faCode}{Programming}{
 {C}, {C++}, {Python}
}

\divider

\cvskills{\faLaptop}{Software}{
  {Arduino}, {Java}, {Python}
}

\divider

\cvskills{\faWrench}{Tools}{
  {Docker}, {Latex}, {Git}, {SublimeText}, {SQL}, {Trello}, {Slack}
}


\end{document}